A Classical Density-Functional Theory for Describing Water Interfaces

### 2011-07-22 paper/project.tex
Changed bohrs to nm in several 1D slit files and in project

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/entropy}
\end{center}
\caption{The free energy, internal energy, and temperature*entropy versus density at room temperature.  }
\label{fig:energy-room-temp}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/entropy-at-690K}
\end{center}
\caption{The free energy, internal energy, and temperature*entropy versus density near the critical temperature.  }
\label{fig:energy-near-critical-temp}
\end{figure}

@@

One of the most computationally simple ways to study confined water is by
constraining it to a slit where the water molecules can only move in one
dimension. We apply a constraining potential of the form

\begin{align}
V = n_l*constraint + 100*n_v (FIXME)
\end{align}

such that the density is 100 times the vapor density outside the slit 
and approximately equal to the saturated liquid density inside. The slits
range in size from 5 bohrs to 150 bohrs (FIX - redo in nm?). We 
minimize the energy and calculate density, energy, and $X$ on a lattice
with a spacing of 0.2 bohrs between data points.

The density profile for a slit of size 60 bohrs is shown in Figure 
\ref{fig:density-1D}. Near the interface, there are oscillations around the 
liquid density which decrease near the center of the slit. We expect the
center of the slit to act approximately like bulk water, and the absence 
of oscillations supports this. For larger slits (~120 bohrs or more) the
majority of the water molecules in the slit act like the bulk. We also 
determine the smallest slit that can contain liquid water, approximately 
30 bohrs. For smaller slits, the initial liquid water inside will vaporize.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/energy-1D}
\end{center}
\caption{ Energy density profile for a slab of water with molecules 
constrained to move in one dimension. }
\label{fig:energy-1D}
\end{figure}

The value of $X$ behaves as expected for water constrained to a slit. We
show in Figure \ref{fig:xassoc-1D} the plot of $X$ for a slit of 60 bohrs.
Outside the slit, there is no hydrogen bonding, and inside $X$ is 
approximately equal to
that of saturated liquid water.

@@

@@

>>>>

% \begin{figure}
% \begin{center}
% \includegraphics[width=\columnwidth]{figs/entropy}
% \end{center}
% \caption{The free energy, internal energy, and temperature*entropy versus density at room temperature.  }
% \label{fig:energy-room-temp}
% \end{figure}
% 
% \begin{figure}
% \begin{center}
% \includegraphics[width=\columnwidth]{figs/entropy-at-690K}
% \end{center}
% \caption{The free energy, internal energy, and temperature*entropy versus density near the critical temperature.  }
% \label{fig:energy-near-critical-temp}
% \end{figure}

@@

@@

One of the most computationally simple ways to study confined water is by
constraining it to a slit where the water molecules can only move in one
dimension. Experimentally, this could represent two different situations.
The first, water between two perfectly aligned and smooth planes, is not common 
in experiment due to the difficulty of creating such an ideal situation. The second
possibility is a large sphere brought close to a plane, which eliminates the 
need for perfect alignment.

We choose a chemical potential corresponding to a pressure of 1 atm and we apply 
a constraining potential where the density is equal to the saturated 
liquid density inside the slit. Outside the slit, we choose a small non-zero
density for numerical reasons. The slits studied range in size from 0.1 nm to 
8.0 nm. We minimize the energy and calculate density, energy, and $X$ on a lattice
with a spacing of approximately 0.01 nm (0.2 bohrs) between lattice points.

The density profile for a slit of size 4.0 nm is shown in Figure 
\ref{fig:density-1D}. Near the interface, there are oscillations around the 
liquid density which decrease near the center of the slit. We expect the
center of the slit to act approximately like bulk water, and the absence 
of oscillations supports this. For larger slits (6.0 nm or more) the
majority of the water molecules in the slit act like the bulk. We also 
determine the smallest slit that can contain liquid water, approximately 
0.6 nm (\textcolor{red}{Check this again}. For smaller slits, the initial 
liquid water inside will vaporize.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/energy-1D}
\end{center}
\caption{ Energy densities for a slab of water with molecules 
constrained to move in one dimension. \textcolor{red}{FIXME}}
\label{fig:energy-1D}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/cavitysize-vs-energy-1D}
\end{center}
\caption{ Free energy versus slit size for a slab of water with molecules 
constrained to move in one dimension. \textcolor{red}{Not sure if this needs
to have a bulk energy amount removed to be accurate.}}
\label{fig:cavitysize-vs-energy-1D}
\end{figure}

The value of $X$ behaves as expected for water constrained to a slit. We
show in Figure \ref{fig:xassoc-1D} the plot of $X$ for a slit of 4.0 nm.
Outside the slit, there is no hydrogen bonding ($X$ = 1), and inside $X$ is 
approximately equal to 0.13, or that of saturated liquid water.

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/energy-vs-diameter}
\end{center}
\caption{ Energy versus diameter for a single hydrophobic rod
immersed in water. This should have an asymptote equal to the surface
tension. (FIXME - Data points are not correct yet) }
\label{fig:energy-vs-diameter}
\end{figure}
